Generation of TypeScript Declaration Files from JavaScript Code

### 2020-08-17 programming-2021/main.tex
Update highlighted box removing comments regarding undefined and question mark token

declare function GreetSettingsModule(settings: GreetSettingsModule.I__settings): void;
declare namespace GreetSettingsModule {
  export interface I__settings {
    'greeting': string;
    'duration' ?: number;
    'color' ?: string;
  }

@@

\begin{changethis}
  We implemented only basic TypeScript features and we focused our effort in building an
  end-to-end solution that generates valid and useful declaration files. Only the basic
  types \texttt{string}, \texttt{number}, \texttt{boolean} and its union were considered
  both for function parameters and interface properties. Common types such as
  \texttt{any}, arrays, function callbacks, tuples, intersections and features such as
  generics, index signatures were not implemented. Each declaration file was tagged with
  \texttt{dts-parse} and those containing unimplemented features were ignored.
\end{changethis}

>>>>

declare function GreetSettingsModule(settings: GreetSettingsModule.I__settings): void;
declare namespace GreetSettingsModule {
  export interface I__settings {
    'greeting': string;
    'duration'?: number;
    'color'?: string;
  }

@@

We implemented only basic TypeScript features and we focused our effort in building an
end-to-end solution that generates valid and useful declaration files. Only the basic
types \texttt{string}, \texttt{number}, \texttt{boolean} and its union were considered
both for function parameters and interface properties. Common types such as
\texttt{any}, arrays, function callbacks, tuples, intersections and features such as
generics, index signatures were not implemented. Each declaration file was tagged with
\texttt{dts-parse} and those containing unimplemented features were ignored.
